Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-10-03 paper.tex
fix another typo
switch to iclr template

%\usepackage{nips_2017}
\usepackage{dsfont}
% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[final]{nips_2017}

@@

The CogSketch~\cite{forbus2011cogsketch} system also aims to have a
high-level understanding of hand-drawn figures. Their primary goal is
cognitive modeling (they apply their system to solving IQ-test
style visual reasoning problems), whereas we are interested in
building an automated AI application (e.g. in our system the user need
not annotate which strokes correspond to which shapes; our neural
network produces something equivalent to the annotations).  A key
similarity however is that both CogSketch and our system have as a
goal to make it easier to produce nice-looking figures.
Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems. The goals of~\cite{ellis2015unsupervised} were cognitive modeling,
and they applied their technique to synthetic scenes used in human behavioral studies.
%% open domain sketch understanding. structure mapping style model. also taps into cyc? the user segments the ink and labels them with concepts from knowledge base. like us they focus on compositional understanding. ``cognitive simulation", solves things like Raven matrices in IQ tests. not really trying right now to be automated like our system.

@@

\section{Synthesizing graphics programs from execution traces}\label{programSynthesisSection}
While the execution trace of a graphics program describes the contents
of a scene, it does not encode higher-level features of the image,
such as repeated motifs or symmetries.  A \emph{graphics
  program} better describe such structures;
we seek to synthesize simple graphics from their execution traces.

>>>>

%\usepackage{nips_2017}
\usepackage{dsfont}
% to compile a camera-ready version, add the [final] option, e.g.:
%\usepackage[final]{nips_2017}
%ICLR packages:
\usepackage{iclr2018_conference,times}

@@

The CogSketch~\cite{forbus2011cogsketch} system also aims to have a
high-level understanding of hand-drawn figures. Their primary goal is
cognitive modeling (they apply their system to solving IQ-test
style visual reasoning problems), whereas we are interested in
building an automated AI application (e.g. in our system the user need
not annotate which strokes correspond to which shapes; our neural
network produces something equivalent to the annotations).
%A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems. The goals of~\cite{ellis2015unsupervised} were cognitive modeling,
and they applied their technique to synthetic scenes used in human behavioral studies.
%% open domain sketch understanding. structure mapping style model. also taps into cyc? the user segments the ink and labels them with concepts from knowledge base. like us they focus on compositional understanding. ``cognitive simulation", solves things like Raven matrices in IQ tests. not really trying right now to be automated like our system.

Synthesizing programs from their execution traces is an old
idea~\cite{Summers:1977:MLP:321992.322002}.  This previous work
departs from our approach in the nature of the problem (synthesizing
recursive algorithms in Lisp vs. graphics programs in~\LaTeX) and the
specifics of the solution (hand-coded source-to-source transformations vs. neural networks
combined with general-purpose program synthesis techniques).
What they share is the use of an execution trace as a
stepping stone toward a full program.

@@

\section{Synthesizing graphics programs from execution traces}\label{programSynthesisSection}
While the execution trace of a graphics program describes the contents
of a scene, it does not encode higher-level features of the image,
such as repeated motifs or symmetries.  A \emph{graphics
  program} better describe such structures;
we seek to synthesize simple graphics programs from their execution traces.
